Lesson 4
========================================================

***

### Scatterplots and Perceived Audience Size
Notes:

***

### Scatterplots
Notes:

```{r Scatterplots}
library(ggplot2)
pf <- read.csv('pseudo_facebook.tsv', sep = '\t')

qplot(x = age, y = friend_count, data = pf)

ggplot(aes(x = age, y = friend_count), data = pf) + geom_point()
```

***

#### What are some things that you notice right away?
Response:

***

### ggplot Syntax
Notes:

```{r ggplot Syntax}
ggplot(aes(x = age, y = friend_count), data = pf) + 
  geom_point() +
  xlim(13, 90)
```

***

### Overplotting
Notes:

```{r Overplotting}
ggplot(aes(x = age, y = friend_count), data = pf) +
  geom_jitter(alpha = 1/20) +
  xlim(13, 90)
```

#### What do you notice in the plot?
Response:

***

### Coord_trans()
### Look up the documentation for coord_trans() and add a layer to the plot that ### transforms friend_count using the square root function. Create your plot

```{r Coord_trans()}
ggplot(aes(x = age, y = friend_count), data = pf) +
  geom_point(alpha = 1/20) +
  xlim(13, 90) +
  coord_trans(y = 'sqrt')
```


### Alpha and Jitter
Notes:

```{r Alpha and Jitter}
ggplot(aes(x= age, y = friend_count), data = pf) +
  geom_point(alpha = 1/20, position = position_jitter(h = 0)) +
  xlim(13, 90) +
  coord_trans(y = 'sqrt')
```

### Examine the relationship between friendships_initiated (y) and age (x)
### using the ggplot synta

```{r}
ggplot(aes(x = age, y = friendships_initiated), data = pf) +
  geom_point(alpha = 1/20, position = position_jitter(h = 0)) +
  xlim(13, 90) +
  coord_trans(y = 'sqrt')
```

***

### Overplotting and Domain Knowledge
Notes:

***

### Conditional Means
Notes:

```{r Conditional Means}
library(dplyr)
age_groups <- group_by(pf, age)
pf.fc_by_age <- summarize(age_groups, 
                          mean_friend_count = mean(friend_count), 
                          median_friend_count = median(friend_count), 
                          n = n())
```

Create your plot!

```{r Conditional Means Plot}
ggplot(aes(x = age, y = mean_friend_count), data = pf.fc_by_age) +
  geom_line() +
  xlim(13, 90)
```

***

### Overlaying Summaries with Raw Data
Notes:

```{r Overlaying Summaries with Raw Data}
ggplot(aes(x = age, y = friend_count), data = pf) +
  geom_point(alpha = 1/20, position = position_jitter(h = 0), color = 'orange') +
  coord_cartesian(xlim = c(13, 90), ylim = c(0, 1000)) +
  geom_line(stat = 'summary', fun.y = mean) +
  geom_line(stat = 'summary', fun.y = quantile, fun.args = list(probs = 0.1), linetype = 2, color = 'blue') +
  geom_line(stat = 'summary', fun.y = quantile, fun.args = list(probs = 0.9), color = 'blue', linetype = 2) +
  geom_line(stat = 'summary', fun.y = median, color = 'blue')

```

#### What are some of your observations of the plot?
Response:

***

### Moira: Histogram Summary and Scatterplot
See the Instructor Notes of this video to download Moira's paper on perceived audience size and to see the final plot.

Notes:

***

### Correlation
Notes:

```{r Correlation}
cor.test(pf$age, pf$friend_count)
```

Look up the documentation for the cor.test function.

What's the correlation between age and friend count? Round to three decimal places.
Response:

***

### Correlation on Subsets
Notes:

```{r Correlation on Subsets}
with(subset(pf, age <= 70), cor.test(age, friend_count))
```

***

### Correlation Methods
Notes:

***

## Create Scatterplots
Notes:

```{r}
ggplot(aes(x = www_likes_received, y = likes_received), data = pf) +
  geom_point(alpha = 1/10, color = 'orange', position = position_jitter(h = 0)) +
  xlim(0, quantile(pf$www_likes_received, 0.95)) +
  ylim(0, quantile(pf$likes_received, 0.95))
```

***

### Strong Correlations
Notes:

```{r Strong Correlations}
ggplot(aes(x = www_likes_received, y = likes_received), data = pf) +
  geom_point(alpha = 1/20, position = position_jitter(h = 0), color = 'orange') +
  xlim(0, quantile(pf$www_likes_received, 0.95)) +
  ylim(0, quantile(pf$likes_received, 0.95)) +
  geom_smooth(method = 'lm', color = 'red')

```

What's the correlation betwen the two variables? Include the top 5% of values for the variable in the calculation and round to 3 decimal places.

```{r Correlation Calcuation}
cor.test(pf$www_likes_received, pf$likes_received)
```

Response:

***

### Moira on Correlation
Notes:

***

### More Caution with Correlation
Notes:

```{r More Caution With Correlation}
library(alr3)
data("Mitchell")
?Mitchell
```

Create your plot!

```{r Temp vs Month}
ggplot(aes(x = Month, y = Temp), data = Mitchell) +
  geom_point()

```

***

### Noisy Scatterplots
a. Take a guess for the correlation coefficient for the scatterplot.

b. What is the actual correlation of the two variables?
(Round to the thousandths place)

```{r Noisy Scatterplots}
cor.test(Mitchell$Month, Mitchell$Temp)
```

***

### Making Sense of Data
Notes:

```{r Making Sense of Data}
ggplot(aes(x = Month, y = Temp), data = Mitchell) +
  geom_point() +
  scale_x_continuous(breaks = seq(0, 203, 12))
```

```{r}
ggplot(aes(x = (Month%%12), y = Temp), data = Mitchell) +
  geom_point()
```

### A New Perspective

***

### Understanding Noise: Age to Age Months
Notes:

```{r Understanding Noise: Age to Age Months}
pf$age_by_month <- pf$age + (12-pf$dob_month)/12
```

***

### Age with Months Means

```{r Age with Months Means}
age_by_month_groups <- group_by(pf, age_by_month)
pf.fc_by_age_month <- summarize(age_by_month_groups,
                                mean_friend_count = mean(friend_count), 
                                median_friend_count = median(friend_count), 
                                n = n())
```

Programming Assignment
```{r Programming Assignment}
ggplot(aes(x = age_by_month, y = mean_friend_count), data = pf.fc_by_age_month) +
  geom_line() +
  xlim(13, 70) +
  ylim(0, 500)
```

***

### Smoothing Conditional Means
Notes:

```{r Smoothing Conditional Means}
library(gridExtra)
p1 <- ggplot(aes(x = age, y = mean_friend_count), data = subset(pf.fc_by_age, age < 71)) +
  geom_line() +
  geom_smooth()

p2 <- ggplot(aes(x = age_by_month, y = mean_friend_count), data = subset(pf.fc_by_age_month, age_by_month < 71)) + 
  geom_line() +
  geom_smooth()

grid.arrange(p1, p2, ncol=1)

```

***

### Analyzing Two Variables

***

Click **KnitHTML** to see all of your hard work and to have an html
page of this lesson, your answers, and your notes!

