Lesson 3
========================================================


### Pseudo-Facebook User Data


```{r Pseudo-Facebook User Data}
pf <- read.csv('pseudo_facebook.tsv', sep = '\t')

names(pf)
```


### Histogram of Users' Birthdays

```{r Histogram of Users\' Birthdays}
library(ggplot2)
qplot(x = dob_day, data = pf, binwidth = 1) + 
  scale_x_continuous(breaks = 1:31)

```

```{r}
ggplot(aes(x = dob_day), data = pf) +
  geom_histogram(binwidth = 1, color = 'white') +
  scale_x_continuous(breaks = 1:31)

```


### Faceting

```{r Faceting}
qplot(x = dob_day, data = pf) +
  scale_x_continuous(breaks = 1:31) +
  facet_wrap(~ dob_month)
```

```{r}
ggplot(aes(x = dob_day), data = pf) +
  geom_histogram(binwidth = 1, color = 'white') +
  scale_x_continuous(breaks = 1:31) +
  facet_wrap(~ dob_month)
```


### Friend Count

#### What code would you enter to create a histogram of friend counts?

```{r Friend Count}
qplot(x = friend_count, data = pf)
ggplot(aes(x = friend_count), data = pf) + geom_histogram()
```


### Limiting the Axes


```{r Limiting the Axes}
qplot(x = friend_count, data = pf, binwidth = 25) + 
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, 50))

ggplot(aes(x = friend_count), data = pf) +
  geom_histogram(binwidth = 25) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, 50))
```


### Faceting Friend Count

```{r Faceting Friend Count}
# What code would you add to create a facet the histogram by gender?
# Add it to the code below.
qplot(x = friend_count, data = pf, binwidth = 10) +
  scale_x_continuous(limits = c(0, 1000),
                     breaks = seq(0, 1000, 50)) +
  facet_wrap(~ gender, ncol = 3)
```


### Omitting NA Values


```{r Omitting NA Values}
qplot(x = friend_count, data = subset(pf, !is.na(gender)), binwidth = 25) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, 50)) +
  facet_wrap(~ gender)

ggplot(aes(x = friend_count), data = subset(pf, !is.na(gender))) +
  geom_histogram(binwidth = 25) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, 50)) +
  facet_wrap(~ gender)
  

```


### Statistics 'by' Gender

```{r Statistics \'by\' Gender}
by(pf$friend_count, pf$gender, summary)

```

### Tenure

```{r Tenure}

qplot(x = tenure, data = pf, color = I('black'), fill = I('#099DD9'), binwidth = 30)

```

```{r}
ggplot(aes(x = tenure), data = pf) + 
  geom_histogram(color = 'black', fill = '#099DD9', binwidth = 30)

```


#### How would you create a histogram of tenure by year?

```{r Tenure Histogram by Year}
qplot(x = tenure/365, data = pf, color = I('black'), fill = I('#099DD9'), binwidth = 0.25) + 
  scale_x_continuous(limits = c(0, 7), breaks = seq(0, 7, 1))

ggplot(aes(x = tenure/365), data = pf) + geom_histogram(binwidth = 0.25, color = 'black', fill = '#099DD9') +
  scale_x_continuous(limits = c(0, 7), breaks = seq(0, 7, 1))

```


### Labeling Plots


```{r Labeling Plots}
qplot(x = tenure/365, data = pf, color = I('black'), fill = I('#099DD9'),
      xlab = 'Number of Years using Facebook', 
      ylab = 'Number of Users in Sample') +
  scale_x_continuous(limits = c(0, 7), breaks = seq(0, 7, 1))

ggplot(aes(x = tenure/365), data = pf) +
  geom_histogram(color = 'black', fill = '#099DD9') +
  scale_x_continuous(limits = c(0, 7), breaks = seq(0, 7, 1)) +
  xlab('Number of Years Using Facebook') +
  ylab('Number of Users in Sample')


```


### User Ages


```{r User Ages}
qplot(x = age, data = pf, color = I('black'), fill = I('#099DD9'), binwidth = 1) +
  scale_x_continuous(limits = c(13, 113), breaks = seq(13, 113, 5))

ggplot(aes(x = age), data = pf) + geom_histogram(binwidth = 1, color = 'black', fill = '#099DD9') +
  scale_x_continuous(limits = c(13, 113), breaks = seq(13, 113, 5))
```


### Add a Scaling Layer


```{r Add a Scaling Layer}
library(gridExtra)
p1 <- qplot(x = friend_count, data = pf, binwidth = 50)
p2 <- qplot(x = friend_count, data = pf, binwidth = 0.1) + scale_x_log10()
p3 <- qplot(x = sqrt(friend_count), data = pf, binwidth = 1)

grid.arrange(p1, p2, p3, ncol = 3)
```

```{r}
p1 <- ggplot(aes(x = friend_count), data = pf) + geom_histogram()
p2 <- p1 + scale_x_log10()
p3 <- p1 + scale_x_sqrt()

grid.arrange(p1, p2, p3, ncol = 3)
```

```{r}
logScale <- qplot(x = log10(friend_count), data = pf)
countScale <- ggplot(aes(x = friend_count), data = pf) + geom_histogram() +
  scale_x_log10()

grid.arrange(logScale, countScale, ncol = 2)

```


### Frequency Polygons

```{r Frequency Polygons}
qplot(x = friend_count, y = ..count../sum(..count..), data = subset(pf, !is.na(gender)), geom = 'freqpoly', color = gender, binwidth = 10) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, 50))

ggplot(aes(x = friend_count, y = ..count../sum(..count..)), data = subset(pf, !is.na(gender))) +
  geom_freqpoly(aes(color = gender), binwidth = 10) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, 50))

```


### Likes on the Web


```{r Likes on the Web}
qplot(x = www_likes, y = ..count../sum(..count..), data = subset(pf, !is.na(gender)), 
                                   geom = 'freqpoly', color = gender) +
        scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, 50))

ggplot(aes(x = www_likes, y = ..count../sum(..count..)), data = subset(pf, !is.na(gender))) +
  geom_freqpoly(aes(color = gender)) +
  scale_x_log10()
  

```


### Box Plots


```{r Box Plots}
qplot(x = gender, y = friend_count, data = subset(pf, !is.na(gender)), geom = 'boxplot')
```

#### Adjust the code to focus on users who have friend counts between 0 and 1000.

```{r}
qplot(x = gender, y = friend_count, data = subset(pf, !is.na(gender)), geom = 'boxplot') + coord_cartesian(ylim = c(0, 1000))
```


### Box Plots, Quartiles, and Friendships


```{r Box Plots, Quartiles, and Friendships}
qplot(x = gender, y = friend_count, data = subset(pf, !is.na(gender)), geom = 'boxplot') + coord_cartesian(ylim = c(0, 250))

by(pf$friend_count, pf$gender, summary)

```

#### On average, who initiated more friendships in our sample: men or women?


```{r Friend Requests by Gender}
qplot(x = gender, y = friendships_initiated, data = subset(pf, !is.na(gender)), geom = 'boxplot') + coord_cartesian(ylim =c(0, 150))

by(pf$friendships_initiated, pf$gender, summary)

```


### Getting Logical


```{r Getting Logical}
pf$mobile_check_in <- ifelse(pf$mobile_likes > 0, 1, 0)
pf$mobile_check_in <- factor(pf$mobile_check_in)
summary(pf$mobile_check_in)
sum(pf$mobile_check_in == 1) / length(pf$mobile_check_in)
```

