Problems Set 4
========================================================

### Price vs.x

```{r}
# In this problem set, you'll continue
# to explore the diamonds data set.

# Your first task is to create a
# scatterplot of price vs x.
# using the ggplot syntax

library(ggplot2)
data(diamonds)

ggplot(aes(x = price, y = x), data = diamonds) +
  geom_point()

```

### Correlation

```{r}
# correlation between price and x
cor.test(diamonds$price, diamonds$x)
```


```{r}
# correlation between price and y
cor.test(diamonds$price, diamonds$y)
```


```{r}
# correlation between price and z
cor.test(diamonds$price, diamonds$z)
```

### Price vs.depth

```{r}
# Create a simple scatter plot of price vs depth
ggplot(aes(x = price, y = depth), data = diamonds) +
  geom_point()
```

### Adjustments-price vs.depth

```{r}
# Change the code to make the transparency of the points to be 1/100 of what they # are now and mark the x-axis every 2 units

ggplot(aes(x = price, y = depth), data = diamonds) +
  geom_point(alpha = 1/100) +
  scale_y_continuous(breaks = seq(40, 80, 2))
```

### Correlation - price and depth

```{r}
cor.test(diamonds$price, diamonds$depth)
```

### Price vs.carat

```{r}
# Create a scatterplot of price vs carat and omit the top 1% of price and carat
# values

ggplot(aes(x = price, y = carat), data = diamonds) + 
  geom_point(alpha = 1/100, position = position_jitter(h = 0)) +
  xlim(0, quantile(diamonds$price, 0.99)) +
  ylim(0, quantile(diamonds$carat, 0.99)) +
  geom_smooth(method = 'lm', color = 'red')
```

### Price vs.volume

```{r}
# Create a scatterplot of price vs. volume (x * y * z).
# This is a very rough approximation for a diamond's volume

diamonds$volume <- diamonds$x * diamonds$y * diamonds$z
ggplot(aes(x = price, y = volume), data = diamonds) +
  geom_point()
```

### Correlations on subsets

```{r}
# What's the correlation of price and volume? Exclude diamonds that have a volume # of zero or that are >= 800
diamonds$right_volume <- (diamonds$volume != 0 & diamonds$volume < 800)
right_diamonds <- subset(diamonds, right_volume)
cor.test(right_diamonds$price, right_diamonds$volume)
```

### Adjustments - price vs.volume

```{r}
# Subset the data to exclude diamonds with a volume greater than or equal to 800 # Also, exclude diamonds with a volume of 0. Adjust the transparency of the
# points and add a linear model to the plot

ggplot(aes(x = price, y = volume), data = subset(diamonds, volume != 0 & volume < 800)) + geom_point(alpha = 1/20, position = position_jitter(h = 0)) + geom_smooth(method = 'lm', color = 'red')
```

### Mean price by clarity

```{r}
# Use the function dplyr package to create a new data frame containing
# info on diamonds by clarity.
# Name the data frame diamondsByClarity
# The data frame should contain the following variables in this order.
#       (1) mean_price
#       (2) median_price
#       (3) min_price
#       (4) max_price
#       (5) n

library(dplyr)
clarity_group <- group_by(diamonds, clarity)
diamondsByClarity <- summarize(clarity_group, 
                               mean_price = mean(price), 
                               median_price = median(price), 
                               min_price = min(price), 
                               max_price = max(price), 
                               n = n())
```

#### Bar charts of mean price

```{r}
diamonds_by_clarity <- group_by(diamonds, clarity)
diamonds_mp_by_clarity <- summarise(diamonds_by_clarity, mean_price = mean(price))

diamonds_by_color <- group_by(diamonds, color)
diamonds_mp_by_color <- summarise(diamonds_by_color, mean_price = mean(price))

# Your task is to write additional code to create two bar plots
# on one output image
library(gridExtra)
p1 <- ggplot(aes(x = clarity, y = mean_price), data = diamonds_mp_by_clarity) +
  geom_bar(stat = 'identity')
p2 <- ggplot(aes(x = color, y = mean_price), data = diamonds_mp_by_color) +
  geom_bar(stat = 'identity')

grid.arrange(p1, p2, ncol=1)
```


### Gapminder revisited

```{r}
# The Gapminder website contains over 500 data sets with information about
# the world's population. Your task is to continue the investigation you did at # # the end of Problem Set 3 or you can start fresh and choose a different data set # from Gapminder.
# In your investigation, examine pairs of variable and create 2-5 plots that make
# use of the techniques from Lesson 4
```

### I am researching the relations between two combinations of variables:

- Literacy Rate vs female primary school completion rate
- Literacy Rate vs Life expectancy


```{r}
library(ggplot2)
library(dplyr)
library(xlsx)
library(rJava)

lit <- read.xlsx('literacy.xlsx', 1)
com <- read.xlsx('Completition rate female.xlsx', 1)

lit <- lit[, c(1, ncol(lit))]
com <- com[, c(1, ncol(com))]

names(lit) <- c('country', 'literacy_rate')
names(com) <- c('country', 'completion_rate')

lit <- lit[complete.cases(lit[,-1]),]
com <- com[complete.cases(com[,-1]),]

lit_com <- inner_join(lit, com, by = 'country')

ggplot(aes(x = completion_rate, y = literacy_rate), data = lit_com) +
  geom_point(color = 'red') +
  geom_smooth(method = 'lm', color = 'orange') +
  xlab('Female Primary School Completion Rate 2011') +
  ylab('Literacy Rate 2011')

cor.test(lit_com$literacy_rate, lit_com$completion_rate)

```

```{r}
life <- read.xlsx('indicator life_expectancy_at_birth.xlsx', 1)
life <- life[complete.cases(life[,1]),]
life <- life[,c(1, grep('X2011',colnames(life)))]
life <- life[complete.cases(life[,-1]),]
names(life) <- c('country', 'life_exp')

lit_life <- inner_join(lit, life, by = 'country')

ggplot(aes(x = literacy_rate, y = life_exp), data = lit_life) +
  geom_point(color = 'orange') +
  geom_smooth(method = 'lm', color = 'red') +
  xlab('Literacy Rate 2011') +
  ylab('Life Expectancy (years)') +
  ggtitle('Literacy vs. Life Expectancy')

```

